---
title: "Sociodemographic characteristics DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the RECORD table(s) to your RStudio environment
# RECORD wave 1, part 1
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_1', 'RECORD.RECORD_w1_1', variables = list('code_barre','Age','sexe','Adm14','Qm3' ))

RECORD_w1_1 <- opal.execute(erasmus_opal,'RECORD_w1_1')

# RECORD wave 1, part 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_2', 'RECORD.RECORD_w1_2', variables = list('code_barre','activite_cgi','nivetude_cgi','q50_rvnu','q48_nbadulte','q49_nbenfant','qm2_recoded','cohab_coup','cohab_seul' )) 
RECORD_w1_2<- opal.execute(erasmus_opal,'RECORD_w1_2')

# RECORD wave 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w2', 'RECORD.RECORD_W2',variables=list('code_barre','age','sexe','Adm14','P54_Q1_1165', 'P54_Q1_1166', 'P57_Q1_1219', 'P57_Q1_1220', 'P57_Q1_1228', 'P57_Q1_1226', 'P57_Q1_1222', 'P57_Q1_1223', 'P57_Q1_1225', 'P57_Q1_1227',  'P57_Q1_1221','P57_Q1_1224','Qm137','P58_Q2_1237','P58_Q1_1234','P56_Q1_1208')) 
RECORD_w2 <- opal.execute(erasmus_opal,'RECORD_w2')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
sdc_RECORD_0 <- data.frame(id = RECORD_w1_1$id)
sdc_RECORD_1 <- data.frame(id = RECORD_w2$id)
```

## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```

# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain)
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Education and income subdomain](#education-and-income-subdomain)
4. [Marital status subdomain](#marital-status-subdomain)
5. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_age_0<- as.integer(RECORD_w1_1$Age)

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_1       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_age_1<- as.integer(RECORD_w2$age)

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_2     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_3     
**Variable description**: Age of the participant.     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_4       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_5     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_6     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_0       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_gender_0<- as.integer(ifelse(RECORD_w1_1$sexe =="F",1, ifelse(RECORD_w1_1$sexe =="H",0,NA)))

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_1       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete   
**Harmonization comment**:  Take gender from baseline.    
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_gender_1<- as.integer(ifelse(RECORD_w2$sexe =="F",1, ifelse(RECORD_w2$sexe =="H",0,NA)))

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_2       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_3       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_4       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_5       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_6       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: sdc_employ_0       
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_employ_0<- as.integer(ifelse(RECORD_w1_2$activite_cgi=="act",1, ifelse(RECORD_w1_2$activite_cgi=="cho" | RECORD_w1_2$activite_cgi=="ret",0,NA)))
```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment  

**Harmonization status**:  impossible  
**Harmonization comment**:   Many variables about employement but cannot be put together and harmonized.  
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_3    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_4    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_5    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_6    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_0     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_retire_0<- as.integer(recode(as.character(RECORD_w1_2$activite_cgi), 'ret'=1,'act'=0,'cho'=0,'div'=0))

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_1     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_retire_1<- as.integer(RECORD_w2$P56_Q1_1208)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_2     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_3     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_4     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_5     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_6      
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age   
**Variable name**: sdc_retire_age_0      
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_1    
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_2    
**Variable description**: Age of the participant at retirement.    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_0       
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_highest_edu_0<- recode(as.integer(RECORD_w1_1$Adm14),'1'=1L, '2'=1L,'3'=1L,
                                        '4'=2L,'5'=3L,'6'=4L, .default = NA_integer_)

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_highest_edu_1<- recode(as.integer(RECORD_w2$Adm14),'1'=1L, '2'=1L,'3'=1L,
                                        '4'=2L,'5'=3L,'6'=4L, .default=NA_integer_)


```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_2     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_3     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_4     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_0       
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_postsec_edu_0<- recode(as.integer(RECORD_w1_1$Adm14),'1'=0L, '2'=0L,'3'=0L,
                                        '4'=0L,'5'=1L,'6'=1L, .default = NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_1     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_postsec_edu_1<- recode(as.integer(RECORD_w2$Adm14),'1'=0L, '2'=0L,'3'=0L,
                                        '4'=0L,'5'=1L,'6'=1L, .default=NA_integer_)
```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_2     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_3     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_4     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_0       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:  France 2007 mean disposable income was not available by OECD. RECORD wave 2 recruitment ended Feb 2008 so used France 2008 mean disposable income (24 197).  
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_income_0<- as.integer(ifelse(RECORD_w1_2$q50_rvnu <"3500",0,1))
```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_1       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:  recruitment wave 2 was from 2011-2015. France 2011 mean disposable income was used (and the only one available from OECD).  
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_income_1<- as.integer(ifelse(RECORD_w2$P57_Q1_1219 == 1 | RECORD_w2$P57_Q1_1220 ==1 | RECORD_w2$P57_Q1_1221 ==1 | RECORD_w2$P57_Q1_1222 ==1, 0, ifelse(RECORD_w2$P57_Q1_1223 == 1 | RECORD_w2$P57_Q1_1224 ==1 | RECORD_w2$P57_Q1_1225 ==1 | RECORD_w2$P57_Q1_1226 ==1 |RECORD_w2$P57_Q1_1227 ==1 | RECORD_w2$P57_Q1_1228 ==1, 1, NA)))
```    
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_2       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_3       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_4       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_5       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_6       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
# Marital status subdomain

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_0      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_1      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_2      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_3        
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_4      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_5      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_6      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_0      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_livstat_0<- as.integer(RECORD_w1_2$cohab_coup)
```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_1      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_livstat_1<- as.integer(RECORD_w2$P54_Q1_1165)

```   
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_2      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_3      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_4      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_5      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_6      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   


# Number of people in household subdomain

### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_0      
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
RECORD_w1_2$q48_nbadulte<- as.integer(RECORD_w1_2$q48_nbadulte)
RECORD_w1_2$q49_nbenfant<- as.integer(RECORD_w1_2$q49_nbenfant)
sdc_RECORD_0$sdc_num_pplhh_0<- as.integer(rowSums(RECORD_w1_2[,c("q48_nbadulte","q49_nbenfant")]))

```  
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_1    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
RECORD_w2$P58_Q2_1237<- as.integer(RECORD_w2$P58_Q2_1237)
RECORD_w2$P58_Q1_1234<- as.integer(RECORD_w2$P58_Q1_1234)
sdc_RECORD_1$sdc_num_pplhh_1<- as.integer(rowSums(RECORD_w2[,c("P58_Q2_1237","P58_Q1_1234")]))

```  
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_2    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_3    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_4    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_0    
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_num_childhh_0<- as.integer(RECORD_w1_2$q49_nbenfant)

```  
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_1     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_num_childhh_1<- as.integer(RECORD_w2$P58_Q2_1237)
```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_childhh_2  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_childhh_3  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_childhh_4  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children 
**Variable name**: sdc_num_child_0  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  complete    
**Harmonization comment**:   (Number of children to be added after cleaning. See region)
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_num_child_0<- as.integer(RECORD_w1_1$Qm3)

```    
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_1  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_num_child_1<- as.integer(RECORD_w2$Qm137)

```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_2  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_3  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children   
**Variable name**: sdc_num_child_4  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Children (biological or adopted) 
**Variable name**: sdc_child_0  
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_0$sdc_num_child_0<- ifelse(as.integer(RECORD_w1_1$Qm3)==0,0,ifelse(as.integer(RECORD_w1_1$Qm3)>0,1,NA))

```    
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_1   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_RECORD_1$sdc_child_1<- ifelse(as.integer(RECORD_w2$Qm137)>0,1,ifelse(as.integer(RECORD_w2$Qm137)==0,0,NA))
```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_2   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_3   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_4   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  